---
title: "lesson_2_2_taylor_swift_day_1"
format: html
---

```{r}
library(tidyverse)
```

## Step 1: Here's data for the whole population

```{r}
enjoyment_matrix =
  matrix(
    data = c(92, 89, 90, 88, 95, 100, 98, 93, 95, 84,
             82, 86, 90, 88, 86, 91, 90, 89, 85, 83,
             80, 74, 80, 67, 81, 82, 76, 77, 74, 65,
             72, 68, 74, 73, 70, 69, 72, 70, 68, 67,
             69, 67, 68, 68, 64, 66, 63, 63, 70, 68),
    nrow = 5,
    byrow = TRUE,
    dimnames = list("row" = 1:5, "column" = 1:10)
  )
enjoyment_matrix
```

It's nice to put the data in "long form" where each column is a variable.

```{r}
enjoyment_data =
  enjoyment_matrix |> 
  as_tibble() |>
  mutate(row = 1:5) |> 
  pivot_longer(!row, names_to = "column", values_to = "enjoyment") |> 
  mutate(column = as.integer(column))
enjoyment_data
```

## Step 2: Here are the 3 randomized sampling methods

### Method #1: Simple Random Sample (SRS)

First get your 10 people with a simple random sampling method:

```{r}
simple_random_sample =
  enjoyment_data |>
  sample_n(10)
simple_random_sample
```

Then calculate the average enjoyment for that sample:

```{r}
simple_random_sample |> 
  pull(enjoyment) |> 
  mean()
```

Then package everything into a function that we can run many times. (Nothing will print out yet, we will use this later)

```{r}
run_SRS = function(i) {
  simple_random_sample =
    enjoyment_data |> 
    sample_n(10)
  simple_random_sample |> 
    pull(enjoyment) |> 
    mean()
}
```

### Method #2: Stratified random sample by row

First get your 10 people a stratified sampling method, 2 for each row:

```{r}
stratified_sample_by_row =
  enjoyment_data |>
  group_by(row) |> 
  sample_n(2)
stratified_sample_by_row
```

Then calculate the average enjoyment for that sample:

```{r}
stratified_sample_by_row |> 
  ## YOUR CODE HERE (see Method #1 for an example)
```

Then package everything into a function that we can run many times. (Nothing will print out yet, we will use this later)

```{r}
run_stratified_by_row = function(i) {
  stratified_sample_by_row =
    enjoyment_data |>
    group_by(row) |> 
    sample_n(2)
  stratified_sample_by_row |> 
    ## YOUR CODE HERE (copy-paste from above)
}
```

### Method #3: Stratified random sample by column

First get your 10 people with a stratified sampling methods, 1 for each column:

```{r}
stratified_sample_by_col =
  enjoyment_data |>
  ## YOUR CODE HERE (see Method #2 for an example)
stratified_sample_by_col
```

Then calculate the average enjoyment for that sample:

```{r}
stratified_sample_by_col |> 
  ## YOUR CODE HERE (see Method #1 for an example)
```

Then package everything into a function that we can run many times. (Nothing will print out yet, we will use this later)

```{r}
run_stratified_by_col = function(i) {
  stratified_sample_by_col =
    enjoyment_data |>
    ## YOUR CODE HERE (copy-paste from above)
  stratified_sample_by_col |> 
    ## YOUR CODE HERE (copy-paste from above)
}
```

## Step 3: Run the experiments

```{r}
n_experiments = 100
srs_means = map_dbl(1:n_experiments, run_SRS)
stratified_by_row_means = map_dbl(1:n_experiments, run_stratified_by_row)
stratified_by_col_means = map_dbl(1:n_experiments, run_stratified_by_col)
"first 10:"
srs_means[1:10]
stratified_by_row_means[1:10]
stratified_by_col_means[1:10]
```

## Step 4: Calculate the true average

To check each method for bias, calculate the true average enjoyment for everyone at the concert.

```{r}
true_average = enjoyment_data |> 
  pull(enjoyment) |> 
  mean()
true_average
```

## Step 4: Graph the results of the experiments

The red vertical line represents the true average enjoyment.

```{r, message=FALSE}
experiment_results =
  tibble(
  "Simple random sample" = srs_means,
  "Stratified by row" = stratified_by_row_means,
  "Stratified by column" = stratified_by_col_means
) |> 
  pivot_longer(everything(), names_to = "method", values_to = "average_enjoyment")

experiment_results |> 
  ggplot(aes(x = average_enjoyment, fill = method)) +
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = true_average, colour = "red") +
  facet_wrap(vars(method), ncol = 1) +
  theme(legend.position = "none")
```

Go back to the worksheet now!!
